Normalized Coherence

### 2019-09-14 Analysis/Normalized_Coherence.Rmd
Tweaks to make it run

---
title: "Normalized Coherence"
author: "Kellen Cresswell"
date: "September 13, 2019"
output: pdf_document
---

@@

```{r}
# Option for number of msig pathways to take from each category
num_msig = 10
# Option for number of random networks to generate (Will generate num_rand-1 networks)
num_rand = 1001
# Construct file name to save the results
run <- 1 # Placeholder for the run ID
fileNameOut <- file.path("./data/Coherence_Results/", paste0("coherence_msig_", num_msig, "_rand_", num_rand, "_", run, ".csv"))
```

@@

```{r}
# Reading in Biogrid data
biogrid = read_tsv("./data/BIOGRID-ALL-3.5.174.mitab.txt")
biogrid = biogrid %>% filter(`Taxid Interactor A` == "taxid:9606" & `Taxid Interactor B` == "taxid:9606")

@@

[??? Why do you read all data at once?]

```{r}
[??? What this function does? Write roxygen help]

@@

```{r}
[??? What this function does? Write roxygen help]
slopes_from_edges = function(edges) {
  edges %>% filter(Internal != 0)  %>%
  group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
  do({
    mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
    data.frame(Slope= coef(mod)[1])
  }) %>% arrange(Slope) %>% filter(Count>4)
}
```

@@

```{r}
[??? What this function does? Write roxygen help]
calc_norm_coherence = function(msig_frame, dis_frame, database, num_msig = 10, num_rand = 10) {
  # Splitting into list by categories 
  Count_Sum = split(msig_frame %>% dplyr::select(Disease,Category, Num_Genes) %>% distinct() , msig_frame$Category)
  coherence_tab = bind_rows()
  #Loop through each disease name and get msig normalization and random normalization factors
  for (i in unique(dis_frame$Disease)) {
    # Get disease specific genes
    dis = dis_frame %>% filter(Disease == i)
    # Get msigdf pathways with cloest number of genes, taking num_msig from each category
    close_nets = bind_rows(lapply(Count_Sum,  function(x) x %>% mutate(Diff = abs(Num_Genes-dis$Count)) %>%
      arrange(Diff) %>% head(.,num_msig)))
    # Subsetting msig to only include close pathways
    msig_sub = msig_frame %>% filter(Disease %in% close_nets$Disease)
    # Take median
    mod_slope = median(msig_sub$Slope)
    # Creating num_rand random networks
    j = 1
    slope_list = list()
    while(j < num_rand) {
    # Empty data frame for disease networks
      diseases = bind_rows()
      # Generate random networks until there as many internal edges as current diseases
      while(nrow(diseases)<dis$Count) {
        # Generate random diseases network from PPI database[??? What this function does?]
        diseases_curr = GeneSample(dis$Count, database, directed = FALSE) 
        # Save internal and external edges
        diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = diseases_curr$internal_connectivity, External = diseases_curr$external_connectivity)
        # Filter out zeros
        diseases_curr = diseases_curr %>% filter(Internal !=0) 
        # Bind together non-zero internal/external edges (If all zero then diseases_curr is null and nothing happens)
        diseases = bind_rows(diseases, diseases_curr)
          }
          # Save slope of current network
          slope_list[[j]] = coef(lm(I(sqrt(External)) ~ I(sqrt(Internal))-1, data = diseases))[[1]]
          # Iterate
          j = j+1

>>>>

---
title: "Normalized Coherence"
author: "Kellen Cresswell"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
# Set up the environment
library(knitr)
opts_chunk$set(cache.path='cache/', fig.path='img/', cache=T, tidy=T, fig.keep='high', echo=F, dpi=100, warnings=F, message=F, comment=NA, warning=F, results='as.is', fig.width = 10, fig.height = 6) #out.width=700, 
library(pander)
panderOptions('table.split.table', Inf)
set.seed(1)
library(dplyr)
options(stringsAsFactors = FALSE)
```

@@

```{r}
# Option for number of msig pathways to take from each category
num_msig = 10
# Option for number of random networks to generate (Will generate num_rand-1 networks)
num_rand = 11
# Construct file name to save the results
run <- 1 # Placeholder for the run ID
fileNameOut <- file.path("./data/Coherence_Results/", paste0("coherence_msig_", num_msig, "_rand_", num_rand, "_", run, ".csv"))
```

@@

```{r}
# Reading in Biogrid data
biogrid = read_tsv("./data/BIOGRID-ALL-3.5.174.mitab.txt.gz")
biogrid = biogrid %>% filter(`Taxid Interactor A` == "taxid:9606" & `Taxid Interactor B` == "taxid:9606")

@@

```{r}
# [??? What this function does? Write roxygen help]

@@

```{r}
# [??? What this function does? Write roxygen help]
slopes_from_edges = function(edges) {
  edges %>% filter(Internal != 0)  %>%
  group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
  do({
    mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
    data.frame(Slope= coef(mod)[1])
  }) %>% arrange(Slope) %>% filter(Count>4)
}
```

@@

```{r}
# [??? What this function does? Write roxygen help]
calc_norm_coherence = function(msig_frame, dis_frame, database, num_msig = 10, num_rand = 10) {
  # Splitting into list by categories 
  Count_Sum = split(msig_frame %>% dplyr::select(Disease,Category, Num_Genes) %>% distinct() , msig_frame$Category)
  coherence_tab = bind_rows()
  #Loop through each disease name and get msig normalization and random normalization factors
  for (i in unique(dis_frame$Disease)) {
    # Get disease specific genes
    dis = dis_frame %>% filter(Disease == i)
    # Get msigdf pathways with cloest number of genes, taking num_msig from each category
    close_nets = bind_rows(lapply(Count_Sum,  function(x) x %>% mutate(Diff = abs(Num_Genes-dis$Count)) %>%
      arrange(Diff) %>% head(.,num_msig)))
    # Subsetting msig to only include close pathways
    msig_sub = msig_frame %>% filter(Disease %in% close_nets$Disease)
    # Take median
    mod_slope = median(msig_sub$Slope)
    # Creating num_rand random networks
    j = 1
    slope_list = list()
    while(j < num_rand) {
    # Empty data frame for disease networks
      diseases = bind_rows()
      # Generate random networks until there as many internal edges as current diseases
      while(nrow(diseases)<dis$Count) {
        # Generate random diseases network from PPI database[??? What this function does?]
        diseases_curr = GeneSample(dis$Count, database, directed = FALSE) 
        # Save internal and external edges
        diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = diseases_curr$internal_connectivity, External = diseases_curr$external_connectivity)
        # Filter out zeros
        diseases_curr = diseases_curr %>% filter(Internal !=0) 
        # Bind together non-zero internal/external edges (If all zero then diseases_curr is null and nothing happens)
        diseases = bind_rows(diseases, diseases_curr)
          }
          # Save slope of current network
          slope_list[[j]] = coef(lm(I(sqrt(External)) ~ I(sqrt(Internal))-1, data = diseases))[[1]]
          # Iterate
          j = j+1
